Accelerating Metagenomic Identification of DNA Sequences Using Artificial Neural Networks

### 2025-05-26 article/main.tex
dodany url
sugmission2, all declarations

\subsubsection*{Author contributions}

P.G and R.N. identified the problem, P.G. designed the approach, downloaded the data, implemented the software, performed numerical experiments, P.G. and R.N. prepared the draft. All authors have read and agreed to the published version of the manuscript.

@@

>>>>

\section{Declarations}

\subsubsection*{Ethics approval and consent to participate}

Not applicable.

\subsubsection*{Consent for publication}

Not applicable.

\subsubsection*{Availability of data and material}

Exquisitor is distributed under the terms of both the MIT license and the Apache License (Version 2.0).
The source code is available at \url{https://github.com/pfgryz/exquisitor}.

\subsubsection*{Competing interests}

Authors delare no competing interests.

@@

\subsubsection*{Authors' contributions}

PG and RN identified the problem, PG designed the approach, downloaded the data, implemented the software, performed numerical experiments, PG and RN prepared the draft. All authors have read and agreed to the published version of the manuscript.

\subsubsection*{Acknowledgements}

Not applicable.
